Figure 3c

### 2017-12-04 inst/cellular_localization_encode/cellular_localization_encode.Rmd
lots of work on figures to improve readability

```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
markdown <- ggplot(data = NULL) +
  geom_point(
    data = stats,
    aes(x = gene_name, y = mean, color = fraction),
    position = position_dodge(width = 1)
  ) +
  facet_wrap(~`Biosample term name`, ncol = 1) +
  geom_errorbar(
    data = stats, 
    aes(x = gene_name, ymax = sd_max, ymin = sd_min, colour = fraction), 
    width = 0,
    position = position_dodge(width = 1)
  ) +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(
    y = "% TPM",
    x = "Gene"
  ) +
  guides(colour = guide_legend(title = "Fraction"))

@@

pdf <- ggplot(data = NULL) +
  geom_point(
    data = stats,
    aes(x = gene_name, y = mean, color = fraction),
    position = position_dodge(width = 1),
    size = 0.5
  ) +
  facet_wrap(~`Biosample term name`, ncol = 1) +
  geom_errorbar(
    data = stats, 
    aes(x = gene_name, ymax = sd_max, ymin = sd_min, colour = fraction), 
    width = 0,
    position = position_dodge(width = 1),
    size = 0.25
  ) +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(
    y = "% TPM",
    x = "Gene"
  ) +
  guides(colour = guide_legend(title = "Fraction"))

figure <- plotPDF(pdf) +
  theme(
    axis.text.y = element_text(size = 4),
    strip.text.x = element_text(size = 5)
  )

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```

>>>>

```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
markdown <- ggplot(data = NULL) +
  geom_point(
    data = stats,
    aes(x = gene_name, y = mean, color = fraction),
    position = position_dodge(width = 1)
  ) +
  facet_wrap(~`Biosample term name`, ncol = 1) +
  geom_errorbar(
    data = stats, 
    aes(x = gene_name, ymax = sd_max, ymin = sd_min, colour = fraction), 
    width = 0,
    position = position_dodge(width = 1)
  ) +
  geom_vline(
    mapping = NULL, 
    xintercept=c(1.5, 2.5), 
    color = "darkgrey", 
    linetype = 3
  ) +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(
    y = "% TPM",
    x = "Gene"
  ) +
  guides(colour = guide_legend(title = "Fraction"))

@@

pdf <- ggplot(data = NULL) +
  geom_point(
    data = stats,
    aes(x = gene_name, y = mean, color = fraction),
    position = position_dodge(width = 0.45),
    size = 0.17
  ) +
  facet_wrap(~`Biosample term name`, ncol = 1) +
  geom_errorbar(
    data = stats, 
    aes(x = gene_name, ymax = sd_max, ymin = sd_min, colour = fraction), 
    width = 0,
    position = position_dodge(width = 0.45),
    size = 0.25
  ) +
  geom_vline(
    mapping = NULL,
    xintercept=c(1.5, 2.5), 
    color = "darkgrey", 
    linetype = 3,
    size = 0.35
  ) +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(
    y = "% TPM",
    x = "Gene"
  ) +
  guides(colour = guide_legend(title = "Fraction"))

figure <- plotPDF(pdf) +
  theme(
    axis.text.y = element_text(size = 4),
    panel.spacing = unit(0.1, "lines"),
    strip.text.x = element_text(size = 5, margin = margin(5.5, 5.5, 2.5, 5.5, unit = "pt"))
  )

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
# ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

### 2017-12-04 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
lots of work on figures to improve readability

#vertical lines and labels
vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    max = max(CI95h),
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI == "miR34a asRNA" ~ 1 - 0.25,
      GOI ==    "miR34a HG" ~ 1 + 0.25
    ),
    xend = case_when(
      GOI == "miR34a asRNA" ~ 2 - 0.25,
      GOI ==    "miR34a HG" ~ 2 + 0.25
    ),
    pFormat = pFormat,
    labelX = 1.5
  )

@@

pdf <- p + 
    geom_point(
    data = stats,
    aes(
      x = Treatment,
      y = mean,
      group = GOI
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    shape = 95,
    colour = "gray20"
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Treatment,
      ymin = CI95l,
      ymax = CI95h,
      group = GOI
    ),
    colour = "gray20",
    size = 0.1,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = labelX,
      y = max + 0.3,
      label = pFormat,
      group = GOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.1,
      xend = xend,
      yend = max + 0.1,
      group = GOI
    ),
    colour="grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
  ))

>>>>

#vertical lines and labels
vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    max = max(CI95h),
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  mutate(max = max + c(0, 0.2, 0, 0)) %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI == "miR34a asRNA" ~ 1 - 0.25,
      GOI ==    "miR34a HG" ~ 1 + 0.25
    ),
    xend = case_when(
      GOI == "miR34a asRNA" ~ 2 - 0.25,
      GOI ==    "miR34a HG" ~ 2 + 0.25
    ),
    pFormat = pFormat,
    labelX = 1.5
  )

@@

pdf <- p + 
  geom_point(
    data = stats,
    aes(
      x = Treatment,
      y = mean,
      group = GOI
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    shape = 95,
    size = 4,
    colour = "gray20"
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Treatment,
      ymin = CI95l,
      ymax = CI95h,
      group = GOI
    ),
    colour = "gray20",
    size = 0.3,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = labelX,
      y = max + 0.4,
      label = pFormat,
      group = GOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.1,
      xend = xend,
      yend = max + 0.1,
      group = GOI
    ),
    colour="grey43",
    size = 0.3,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
  ))

### 2017-12-04 inst/hct116_p53_null/hct116_p53_null.Rmd
lots of work on figures to improve readability

pdf <- p + 
  geom_point(
    data = stats,
    aes(x = Treatment, y = mean, group = Condition), 
    position = position_dodge(width = 0.9),
    colour = "gray20",
    shape = 95
  ) +
  geom_linerange(
    data = stats,
    aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(x = Treatment, y = max + 0.28, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
    colour="grey43",
    size = 0.1,
    show.legend = FALSE
  )   +
  guides(
    fill = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 4)
    )
  )

>>>>

pdf <- p + 
  geom_point(
    data = stats,
    aes(x = Treatment, y = mean, group = Condition), 
    position = position_dodge(width = 0.9),
    colour = "gray20",
    shape = 95,
    size = 4
  ) +
  geom_linerange(
    data = stats,
    aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(x = Treatment, y = max + 0.4, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
    colour="grey43",
    size = 0.3,
    show.legend = FALSE
  )   +
  guides(
    fill = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 4)
    )
  )

### 2017-12-04 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
lots of work on figures to improve readability

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = construct,
      ymin = CI95l,
      ymax = CI95h,
      group = plotGene
    ),
    colour = "grey20",
    size = 0.1,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = construct,
      y = mean,
      group = plotGene
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    colour = "gray20",
    shape = 95
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.25, 
      label = pFormat, 
      group = gene
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(fill = guide_legend(
    title = "Gene", 
    override.aes = list(size = 4)
  ))

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = construct,
      ymin = CI95l,
      ymax = CI95h,
      group = plotGene
    ),
    colour = "grey20",
    size = 0.3,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = construct,
      y = mean,
      group = plotGene
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    colour = "gray20",
    size = 4,
    shape = 95
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.35, 
      label = pFormat, 
      group = gene
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.3,
    show.legend = FALSE
  ) +
  guides(fill = guide_legend(
    title = "Gene", 
    override.aes = list(size = 4)
  ))

### 2017-12-04 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
fixing headers in Rmds
adding sessionInfo to all rmds
lots of work on figures to improve readability

stats <- stats %>%
  mutate(plotGOI = case_when(
    GOI == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    GOI == "Renilla" ~ "       Renilla\n(miR34a asRNA)"
  ))

@@

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = treatment, 
      y = log2fold, 
      group = interaction(plotGOI, treatment)
    ),
    trim = TRUE,
    scale = "width",
    alpha = 0.3,
    colour = NA,
    fill = "gray",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = treatment,
      y = log2fold,
      fill = plotGOI
    ),
    binwidth = 1/10,
    alpha = 0.5,
    colour = NA,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  facet_grid(. ~ shRNA, scale = "free") +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Doxorubicin (ng/ml)",
    title = "HCT116"
  )

markdown <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = CI95h + 0.2,
      label = pFormat,
      group = plotGOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    position = position_dodge(width = 0.9),
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 6)
    )
  )

@@

pdf <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = CI95h + 0.2,
      label = pFormat,
      group = plotGOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    position = position_dodge(width = 0.9),
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  ) +
  guides(fill = guide_legend(
    title = "Gene",
    override.aes = list(size = 4)
  ))

>>>>

stats <- stats %>%
  mutate(plotGOI = case_when(
    GOI == "Luciferase" ~ " Luciferase\n(miR34a HG)",
    GOI == "Renilla" ~ "  Renilla\n(miR34a asRNA)"
  )) %>%
  group_by(GOI, treatment) %>%
  mutate(
    height = if_else(treatment == 0, 0, max(CI95h, na.rm = TRUE)),
    x = case_when(
      treatment ==   0 ~ 1 + 0.25,
      treatment == 300 ~ 2 + 0.25,
      treatment == 500 ~ 3 + 0.25
    ),
    xend = case_when(
      treatment ==   0 ~ 1 - 0.25,
      treatment == 300 ~ 2 - 0.25,
      treatment == 500 ~ 3 - 0.25
    )
  ) %>%
  ungroup()
```

@@

# p <- ggplot(data = NULL) +
#   geom_violin(
#     data = data,
#     aes(
#       x = treatment, 
#       y = log2fold, 
#       group = interaction(plotGOI, treatment)
#     ),
#     trim = TRUE,
#     scale = "width",
#     alpha = 0.3,
#     colour = NA,
#     fill = "gray",
#     show.legend = FALSE
#   ) +
#   geom_dotplot(
#     data = data, 
#     aes(
#       x = treatment,
#       y = log2fold,
#       fill = plotGOI
#     ),
#     binwidth = 1/10,
#     #alpha = 0.5,
#     colour = NA,
#     position = position_dodge(width = 0.9), 
#     binaxis = 'y', 
#     stackdir = 'center',
#     dotsize = 2,
#     show.legend = TRUE
#   ) +
#   facet_grid(. ~ shRNA, scale = "free") +
#   scale_y_continuous("\u0394\u0394Ct") +
#   labs(
#     x = "Doxorubicin (ng/ml)",
#     title = "HCT116"
#   )

# markdown <- p + 
#   geom_linerange(
#     data = stats,
#     aes(
#       x = treatment, 
#       ymin = CI95l, 
#       ymax = CI95h, 
#       group = plotGOI
#     ),
#     colour = "gray20",
#     position = position_dodge(width = 0.9),
#     show.legend = FALSE
#   ) +
#   geom_point(
#     data = stats,
#     aes(
#       x = treatment, 
#       y = mean, 
#       group = plotGOI
#     ),
#     colour = "gray20",
#     position = position_dodge(width = 0.9),
#     shape = 95,
#     size = 6,
#     show.legend = FALSE
#   ) +
#   geom_label(
#     data = stats,
#     aes(
#       x = treatment, 
#       y = CI95h + 0.2,
#       label = pFormat,
#       group = plotGOI
#     ),
#     label.size = 0,
#     label.padding = unit(0.01, "lines"),
#     show.legend = FALSE,
#     position = position_dodge(width = 0.9),
#     fill = "white",
#     size = 5,
#     family = "Arial Unicode MS"
#   ) +
#   guides(
#     fill = guide_legend(
#       title = "Gene", 
#       override.aes = list(size = 6)
#     )
#   )

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = treatment, 
      y = log2fold, 
      group = interaction(shRNA, treatment)
    ),
    trim = TRUE,
    scale = "width",
    alpha = 0.3,
    colour = NA,
    fill = "gray",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = treatment,
      y = log2fold,
      fill = shRNA
    ),
    binwidth = 1/10,
    #alpha = 0.5,
    colour = NA,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  facet_grid(. ~ plotGOI, scale = "free") +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Doxorubicin (ng/ml)",
    title = "HCT116"
  )
markdown <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = shRNA
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = shRNA
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = height + 0.5,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = height + 0.25, xend = xend, yend = height + 0.25),
    colour="grey43",
    show.legend = FALSE
  )  +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 6)
    )
  )

@@

pdf <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = shRNA
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = shRNA
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 4,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = height + 0.5,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = height + 0.25, xend = xend, yend = height + 0.25),
    colour="grey43",
    size = 0.3,
    show.legend = FALSE
  )  +
  guides(fill = guide_legend(
    title = "Gene",
    override.aes = list(size = 4)
  ))

### 2017-12-04 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
lots of work on figures to improve readability

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = phase, 
      y = value,
      group = interaction(phase, condition)
    ),
    scale = "width",
    alpha = 0.3,
    fill = "gray",
    weight = 10,
    trim = TRUE,
    color = NA,
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = phase,
      y = value,
      fill = condition
    ),
    binwidth = 1/100,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 0.5,
    show.legend = TRUE
  ) +
  facet_grid(
    . ~ `Cell line`, 
    scale = "free"
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = "Cell cycle phase",
    y = "",
    title = "Cell cycle"
  )

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = phase, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = interaction(phase, condition)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey25",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = phase, 
      y = mean, 
      group = condition
    ), 
    colour = "black",
    position = position_dodge(width = 0.9),
    shape = 95,
    show.legend = FALSE
  ) +
  geom_segment(
    data = stats,
    aes(
      x = x,
      y = y + 0.01, 
      xend = xend, 
      yend = y + 0.01
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = phase, 
      y = y + 0.025, 
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  ) +
  guides(
    fill = guide_legend(
      title = "Condition", 
      override.aes = list(size = 4)
    )
  )

>>>>

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = phase, 
      y = value,
      group = interaction(phase, condition)
    ),
    scale = "width",
    alpha = 0.3,
    fill = "gray",
    weight = 10,
    trim = TRUE,
    color = NA,
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = phase,
      y = value,
      fill = condition
    ),
    binwidth = 1/100,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 1,
    show.legend = TRUE
  ) +
  facet_grid(
    . ~ `Cell line`, 
    scale = "free"
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = "Cell cycle phase",
    y = "",
    title = "Cell cycle"
  )

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = phase, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = interaction(phase, condition)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey25",
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = phase, 
      y = mean, 
      group = condition
    ), 
    colour = "black",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 4,
    show.legend = FALSE
  ) +
  geom_segment(
    data = stats,
    aes(
      x = x,
      y = y + 0.01, 
      xend = xend, 
      yend = y + 0.01
    ),
    colour = "grey43",
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = phase, 
      y = y + 0.025, 
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  ) +
  guides(
    fill = guide_legend(
      title = "Condition", 
      override.aes = list(size = 4)
    )
  )

### 2017-12-04 inst/stable_line_expression/stable_line_expression.Rmd
lots of work on figures to improve readability

vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI ==    "miR34a" ~ 1 + 0.25,
      GOI == "miR34a asRNA" ~ 1 - 0.25
    ),
    xend = case_when(
      GOI ==    "miR34a" ~ 2 + 0.25,
      GOI == "miR34a asRNA" ~ 2 - 0.25
    )
  ) %>%
  inner_join(ys) %>%
  mutate(
    max = max + c(0.55, 1.95, 0.25, 1.65, 0.25, 1.65)
  )
```

@@

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = `Genetic mod`,
      y = log2fold,
      group = interaction(`Genetic mod`, GOI)
    ),
    trim = TRUE,
    alpha = 0.5,
    fill = "grey",
    colour = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = `Genetic mod`,
      y = log2fold,
      fill = GOI,
      group = interaction(`Genetic mod`, GOI)
    ),
    binwidth = 1/10,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  facet_grid(
    . ~ `Cell line`, 
    scales = "free", 
    space = "free"
  ) +
  scale_y_continuous("\u0394\u0394Ct")+
  labs(x = "Cell line")

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = `Genetic mod`,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(`Genetic mod`, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = `Genetic mod`,
      y = mean,
      group = interaction(`Genetic mod`, GOI)
    ),
    colour = "gray20",
    shape = 95,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.6, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 1.5
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

>>>>

vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI ==    "miR34a" ~ 1 + 0.25,
      GOI == "miR34a asRNA" ~ 1 - 0.25
    ),
    xend = case_when(
      GOI ==    "miR34a" ~ 2 + 0.25,
      GOI == "miR34a asRNA" ~ 2 - 0.25
    )
  ) %>%
  inner_join(ys) %>%
  mutate(
    max = max + c(0.75, 2.65, 0.45, 2.35, 0.45, 2.35)
  )
```

@@

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = `Genetic mod`,
      y = log2fold,
      group = interaction(`Genetic mod`, GOI)
    ),
    trim = TRUE,
    alpha = 0.5,
    fill = "grey",
    colour = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = `Genetic mod`,
      y = log2fold,
      fill = GOI,
      group = interaction(`Genetic mod`, GOI)
    ),
    binwidth = 1/10,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 6,
    show.legend = TRUE
  ) +
  facet_grid(
    . ~ `Cell line`, 
    scales = "free", 
    space = "free"
  ) +
  scale_y_continuous("\u0394\u0394Ct")+
  labs(x = "Cell line")

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = `Genetic mod`,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(`Genetic mod`, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = `Genetic mod`,
      y = mean,
      group = interaction(`Genetic mod`, GOI)
    ),
    colour = "gray20",
    shape = 95,
    size = 4,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.85, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 2
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.3,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

### 2017-12-04 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
lots of work on figures to improve readability

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    lwd = 0.1,
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    size = 0.25,
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) + 
  guides(
    colour = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 2)
    )
  )

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    lwd = 0.2,
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    size = 0.25,
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) + 
  guides(
    colour = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 2)
    )
  )
